Red, Blue, or Grey? 2024’s Battleground States Tell a Story

### 2024-11-04 paper/paper.qmd
paper final draft

---
title: "Red, Blue, or Purple? 2024’s Battleground States Tell a Story"
subtitle: "Pennsylvania, Ohio, and Nevada Become Game Changers as Trump Gains Ground"
author: 
  - Yingke He
  - Ziheng Zhong
thanks: "Code and data are available at: [https://github.com/iJustinn/Election_Prediction.git](https://github.com/iJustinn/Election_Prediction.git)."
date: today
date-format: long
abstract: "This paper presents an analysis of polling data for the 2024 U.S. Presidential election, focusing on key candidates, notably Donald Trump and Kamala Harris, to provide an in-depth assessment of the race. Employing a Hierarchical Bayesian Model, the study shows substantial state-level variations, with Pennsylvania, Ohio, Georgia, and Nevada identified as pivotal battlegrounds that show a tendency to lean toward Trump. These findings emphasize the dynamic and shifting landscape of U.S. politics and underscore the key impact of swing states on election results."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

The study's main objective is to estimate state-level vote shares for each candidate, taking into account variables such as regional differences, pollster-specific biases, and the timing of polls relative to Election Day (@citePolls). Key predictors—including polling percentages, sample sizes, and days remaining until the election—are incorporated into the model, which adjusts for variations by state and pollster. The Hierarchical Bayesian Model was selected for its capability to capture intricate data patterns, enabling accurate vote share estimations that mirror the distribution of polling data across diverse U.S. regions.

>>>>

---
title: "Red, Blue, or Grey? 2024’s Battleground States Tell a Story"
subtitle: "Pennsylvania, Ohio, and Nevada Become Game Changers as Trump Gains Ground"
author: 
  - Yingke He
  - Ziheng Zhong
thanks: "Code and data are available at: [https://github.com/iJustinn/Election_Prediction.git](https://github.com/iJustinn/Election_Prediction.git)."
date: today
date-format: long
abstract: "This paper presents an analysis of polling data for the 2024 U.S. Presidential election, focusing on the key candidates, Donald Trump and Kamala Harris, to provide an in-depth assessment of the race. Employing a Hierarchical Bayesian Model, the study shows substantial state-level variations, with Pennsylvania, Ohio, Georgia, and Nevada identified as pivotal battlegrounds that show a tendency to lean toward Trump. These findings emphasize the dynamic and shifting landscape of U.S. politics and underscore the key impact of swing states on election results."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

The study's main objective is to estimate state-level vote shares for Trump and Harris, taking into account variables such as regional differences, pollster-specific biases, and the timing of polls relative to Election Day (@citePolls). Key predictors—including polling percentages, sample sizes, and days remaining until the election—are incorporated into the model, which adjusts for variations by state and pollster. The Hierarchical Bayesian Model was selected for its capability to capture intricate data patterns, enabling accurate vote share estimations that mirror the distribution of polling data across diverse U.S. regions.
